---
title: "HW1"
author: "Ruwen Zhou"
date: 2019-09-10
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
```
I'm an R Markdown document

# Homework 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}

hw_df = 
  tibble(
    data1 = rnorm(10),
    samp_gt_0 = data1 > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "high", "high", "high", "high"))
  )
```

```{r}
mean(pull(hw_df, data1))
mean(pull(hw_df, samp_gt_0))
mean(pull(hw_df, char_vec))
mean(pull(hw_df, factor_vec))
```

We can take the mean of numbers and logical, but cannot compute the mean of vectors or factors.

```{r}
as.numeric(pull(hw_df, data1))
as.numeric(pull(hw_df, samp_gt_0))
as.numeric(pull(hw_df, char_vec))
as.numeric(pull(hw_df, factor_vec))
```

Numeric, logical and factor can be converted to numeric, but vector cannot.

```{r}
as.numeric(pull(hw_df, samp_gt_0)) * pull(hw_df, data1)
as.factor(pull(hw_df, samp_gt_0)) * pull(hw_df, data1)
as.numeric(as.factor(pull(hw_df, samp_gt_0))) * pull(hw_df, data1)
```



# Homework 2

```{r}

data("penguins", package = "palmerpenguins")
head(penguins)
nrow(penguins)
ncol(penguins)
mean(pull(penguins, flipper_length_mm),na.rm = TRUE)


```
This dataset contains `r nrow(penguins)` penguins and `r ncol(penguins)` variables: species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, bill_depth_mm, body_mass_g, sex, year. The mean of flipper length is `r mean(pull(penguins, flipper_length_mm),na.rm = TRUE)`.

```{r}
plot_df = tibble(
  y = pull(penguins, flipper_length_mm),
  x = pull(penguins, bill_length_mm))

ggplot(plot_df, aes(x = x, y = y, color = pull(penguins,species))) + geom_point()
```







